---
title: "gapminder-analysis"
author: "Blanca Obregon"
date: "January 28, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Let's download the dataset to a CSV file

```  {r }

download.file("https://raw.githubusercontent.com/swcarpentry/r-novice-gapminder/gh-pages/_episodes_rmd/data/gapminder_data.csv", destfile = "data/gapminder_data.csv")

```
## Now, let read the file into R enviro

``` {r }

gapminder <- read.csv("data/gapminder_data.csv")
gapminder


```
Let's display

``` {r }
getwd()

```
## Let's visualize the data

``` {r }

head(gapminder)
```
some more data

``` {r }

tail(gapminder)
```

## Let's plot it


``` {r }

library(ggplot2)
```

### How does life expectancy change with GDP per capita?

``` {r }
ggplot(data = gapminder, mapping=aes(x=gdpPercap, y=lifeExp)) + geom_point()

```
### Let's normalize the data

``` {r }
ggplot(data = gapminder, mapping=aes(x=gdpPercap, y=lifeExp)) + geom_point() + scale_x_log10()

```
### Let's normalize the data and trace a line

``` {r }
ggplot(data = gapminder, mapping=aes(x=gdpPercap, y=lifeExp)) + geom_point(size=.5,alpha=.25) + scale_x_log10() + geom_smooth(method = "lm", size = 1.5)

```

### How does life expectancy change per year?

``` {r }

ggplot(data = gapminder, mapping=aes(x=year, y=lifeExp, by=country, color=continent)) + geom_line() + geom_point() + scale_color_manual(values = c("purple","orange","red","gray","green"))
```
## Avoiding to color the dots

``` {r }

ggplot(data = gapminder, mapping=aes(x=year, y=lifeExp, by=country)) + geom_line(mapping=aes(color=continent)) + geom_point() + scale_color_manual(values = c("purple","orange","red","gray","green"))
```
## Let's select only America Continent

``` {r }

americas <- gapminder[gapminder$continent == "Americas",]
americas
```
### Let's plot

``` {r }
ggplot(data=americas,mapping= aes(x=year, y=lifeExp)) + geom_line() + facet_wrap(~country) + theme(axis.text.x = element_text(angle=90))
```
```

``` {r }

ggsave(plot-lifeExp_plot, filename = "images/lifeExp.png")
```

